HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex
sss

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{emnlp2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}

\def\emnlppaperid{***}

\makeatletter
\renewcommand{\paragraph}{
  \@startsection{paragraph}{4}
  {\z@}{.3ex \@plus .3ex \@minus .2ex}{-1em}
  {\normalfont\normalsize\bfseries}
}
\makeatother

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The HUME Measure}\label{sec:hume}

@@

\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=1\textwidth]{hume_interface2.jpg}
    \caption{The HUME annotation tool. The top orange box
      contains the translation. The source sentence is directly below it, followed by the tree of the source
      semantic units. Alignments between the source and translation are in italics and
      unaligned intervening words are in red (see text).}
    \label{fig:interface}
    \end{center}
\end{figure*}

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}.  These were trained on large parallel data sets extracted from
OPUS \parcite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \parcite{bojar-EtAl:2014:W14-33}, 
giving between 
45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...

These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland, Cochrane is an international NGO
which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' in the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

@@

The source sentences are all in English, and their UCCA annotation was performed by four
computational linguists and one linguist.
For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech. For Czech IAA,
several further annotators worked on a small number of 
sentences each. We treat these further annotators as one annotator, resulting in two annotators
for each language pair.
The annotators were all native speakers of the respective target languages and fluent in English.

\tabref{tab:annot}
shows the total number of sentences and units annotated by each annotator. Note
that not all units in all sentences were annotated, often
due to
%this was because
the annotator not finishing a sentence or accidentally missing a node.
%, but in many cases it was also because it was an implicit 
%UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
Units & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
\caption{Number of HUME-annotated sentences and units.}
\label{tab:annot}
}
\end{center}
\end{table}

@@

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All units & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic units & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural units & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data,
measured by Cohen's Kappa. }
\label{tab:iaa}
}
\end{center}
\end{table}

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
%For German, Polish and Romanian we used two annotators, with a significant overlap
%between the sentences they annotated. For Czech we had the entire batch
%annotated by one main annotator and multiple secondary annotators, 
%each annotating a sub-part of the batch.
\tabref{tab:iaa} reports the number of units which have two annotations from
different annotators and the corresponding Kappas.
%
%In order to compute Kappa, we consider the annotation task as a classification task on 
%nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
units (annotated as Red, Orange or Green) and structural units (annotated
as Adequate or Bad).
As expected and confirmed by confusion matrices in \figref{fig:heatmap}, there
is generally little confusion between the two types of units.

@@

%%%% UNTIL HERE %%%%
\paragraph{Alignment.}
In HMEANT, the alignment between the reference and translation structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and of an accurate translation
still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations at the alignment stage,
to avoid unduly penalization due to such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue was seen by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
IAA on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

%HUME uses only automatic (word-level) alignment, which only serves as a cue for directing
%the attention of the annotators.
%The user is expected to mentally correct the alignment as needed.
HUME uses automatic (word-level) alignment, which only
serves as a cue for directing the attention of the annotators.
The user is expected to mentally correct the
alignment as needed, thus circumventing this difficulty.

\paragraph{Monolingual vs. Bilingual Evaluation}
\label{src-vs-ref}
HUME diverges from HMEANT (and also from the shallow automatic measures
like BLEU or METEOR) in not requiring a reference.
Instead, it compares the source directly with the output translation.

This requires us to employ bilingual annotators, but has the benefit of avoiding
the reference translation. It is known that the reference translations are not
always literal enough and the MT output semantics can be composed differently
than the semantics of the reference.

If only monolingual annotators are available, the HUME evaluation could be performed
with a reference sentence instead of with the source. 
\bh{But this would be a different metric}
% While HUME avoids this problem,
%imposing a structure only on the source does prevent any fine-grained semantic
%analysis of the translation.

@@

\paragraph{Localisation of the Error}

In HMEANT, an error in a child node often results in the parent node
being penalised as well. This makes it harder to quantify the true scale of  
the original error, as its effect gets propagated up the tree. 
In HUME, errors are localised as much as possible to where they occur,
by the separation of atomic and structural units (See Fig \ref{fig:hume_tree_v2} 
for an example).
This allows us to calculate the total score of the sentence more accurately.

@@

We have introduced HUME, a human semantics based MT evaluation measure which addresses
a wide range of semantic phenomena. We have shown that it can be efficiently and 
reliably annotated in 
several languages, and that annotation quality is robust to sentence length.
We believe that HUME, and a future automated version of HUME, will be able to guide the
development of a more semantically aware approach to MT.

>>>>

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{emnlp2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}

\def\emnlppaperid{***}
\setlength{\belowcaptionskip}{-10pt}

\makeatletter

\titlespacing*{\section}
{0pt}{1ex plus 1ex minus .2ex}{1ex plus .2ex}
\titlespacing*{\subsection}
{0pt}{1ex plus 1ex minus .2ex}{1ex plus .2ex}

\renewcommand{\paragraph}{
  \@startsection{paragraph}{4}
  {\z@}{.1ex \@plus .1ex \@minus .1ex}{-1.5em}
  {\normalfont\normalsize\bfseries}
}
\makeatother

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-.1em}
\section{The HUME Measure}\label{sec:hume}
\vspace{-.2em}

@@

\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=.8\textwidth]{hume_interface2.jpg}
    \caption{The HUME annotation tool. The top orange box
      contains the translation. The source sentence is directly below it, followed by the tree of the source
      semantic units. Alignments between the source and translation are in italics and
      unaligned intervening words are in red (see text).}
    \label{fig:interface}
    \end{center}
\end{figure*}

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}.  These were trained on large parallel data sets extracted from
OPUS \parcite{tiedemann:2009}, and the data sets released for the WMT14
medical translation task \parcite{bojar-EtAl:2014:W14-33}, 
giving between 45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...
These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland, Cochrane is an international NGO
which provides independent systematic reviews on health-related research.
NHS~24 texts come from the ``Health A-Z'' section in the NHS Inform
website, and Cochrane texts come from their plain language summaries
and abstracts.

@@

The source sentences are all in English, and their UCCA annotation was performed by four
computational linguists and one linguist.
For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech. For Czech IAA,
several further annotators worked on a small number of 
sentences each. We treat these further annotators as one annotator, resulting in two annotators
for each language pair.
The annotators were all native speakers of the respective target languages and fluent in English.
\oa{maybe we should put in what training they've received}

\tabref{tab:annot}
shows the total number of sentences and units annotated by each annotator.
Not all units in all sentences were annotated, often due to
the annotator %not finishing a sentence or
accidentally missing a node.
%, but in many cases it was also because it was an implicit 
%UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
\#Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
\#Units & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
\caption{HUME-annotated \#sentences and \#units.}
\label{tab:annot}
}
\end{center}
\end{table}

@@

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All units & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic units & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural units & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{IAA for the multiply-annotated units,
measured by Cohen's Kappa. }
\label{tab:iaa}
}
\end{center}
\end{table}

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated units.
%For German, Polish and Romanian we used two annotators, with a significant overlap
%between the sentences they annotated. For Czech we had the entire batch
%annotated by one main annotator and multiple secondary annotators, 
%each annotating a sub-part of the batch.
\tabref{tab:iaa} reports the number of units which have two annotations from
different annotators and the corresponding Kappas.
%
%In order to compute Kappa, we consider the annotation task as a classification task on 
%nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
units (annotated as Red, Orange or Green) and structural units (annotated
as Adequate or Bad).
As expected and confirmed by confusion matrices in \figref{fig:heatmap}, there
is generally little confusion between the two types of units.

@@

\paragraph{Alignment.}
In HMEANT, the alignment between the reference and translation structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and of an accurate translation
still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow modifications to
the SRL annotations at the alignment stage,
to avoid unduly penalization due to such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue is noted in \parcite{lo:wu:reliability:2014}:
the IAA on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.
HUME uses automatic (word-level) alignment, which only
serves as a cue for directing the attention of the annotators.
The user is expected to mentally correct the
alignment as needed, thus circumventing this difficulty.

%HUME uses only automatic (word-level) alignment, which only serves as a cue for directing
%the attention of the annotators.
%The user is expected to mentally correct the alignment as needed.

\paragraph{Monolingual vs. Bilingual Evaluation.}
\label{src-vs-ref}
HUME diverges from both HMEANT and from shallower automatic measures
like BLEU or METEOR, in not requiring a reference.
Instead, it compares the source directly with the output translation.
This requires us to employ bilingual annotators, but has the benefit of avoiding
using a reference. Reference translations may often be phrased in many structurally different
ways, which may again lead unduly penalization of the translation in cases where
it is a paraphrase of the reference.

%If only monolingual annotators are available, the HUME evaluation could be performed
%with a reference sentence instead of with the source. 
%\bh{But this would be a different metric}

% While HUME avoids this problem,
%imposing a structure only on the source does prevent any fine-grained semantic
%analysis of the translation.

@@

\com{
\paragraph{Error Localisation.}
In HMEANT, an error in a child node often results in the parent node
being penalised as well. This makes it harder to quantify the true scale of  
the original error, as its effect gets propagated up the tree. 
In HUME, errors are localised as much as possible to where they occur,
by the separation of atomic and structural units,
which supports a more accurate aggregation of the translation errors
to a composite score.
}
\oa{Omitted point here}

@@

We have introduced HUME, a human semantic MT evaluation measure which addresses
a wide range of semantic phenomena. We have shown that it can be reliably and 
efficiently annotated in multiple languages,
and that annotation quality is robust to sentence length.
We believe that
HUME, and a future automated version of HUME, allows for a more fine-grained analysis of translation quality,
and will be to guide the development of a more semantically aware approach to MT.
